Iterative Monomorphisation

### 2024-01-31 iterative_monomorphisation.tex
changes

\copyrightyear{2024}
\copyrightclause{standard copyright text (cc logo is placeholder)}

\conference{not a conference}

@@

\author[1]{Jasmin Blanchette}[%
email=jasmin.blanchette@ifi.lmu.de,
url=https://www.tcs.ifi.lmu.de/mitarbeiter/jasmin-blanchette_de.html,
]
\address[1]{lmu}
\author{Sascha B\"ohme}[%
email=sascha.boehme@posteo.de,
]
\author[1,2]{Tanguy Bozec}[%
email=tanguy.bozec@ens-paris-saclay.fr,
]
\address[2]{ens paris-saclay}

@@

\begin{keywords}
   monomorphisation\sep
   higher order theorem proving \sep
   automatic theorem proving
\end{keywords}

>>>>

\copyrightyear{2024}
\copyrightclause{Copyright for this paper by its authors. Use permitted under Creative Commons License Attribution 4.0 International (CC BY 4.0)}

\conference{Submitted draft} % TODO update

@@

\author[1,2]{Tanguy Bozec}[%
email=tanguy.bozec@ens-paris-saclay.fr,
]
\author[2]{Jasmin Blanchette}[%
email=jasmin.blanchette@ifi.lmu.de,
%url=https://www.tcs.ifi.lmu.de/mitarbeiter/jasmin-blanchette_de.html,
]
\address[1]{Departement d'informatique, École normale supérieure Paris-Saclay, France} % TODO dpt info
\address[2]{Institute of Informatics, Ludwig-Maximilians-Universität München, Germany}

@@

\begin{keywords}
   polymorphism\sep
   higher order logic\sep
   automatic theorem proving
\end{keywords}
